### 2010-03-11 papers/icfp-2010-desc/paper_type_theory.tex
Desc@ICFP: close section Levitation.
Desc@ICFP: fix \cite{} which was preventing compilation on ancient version of pdflatex.

\subsection{Finite sets}

@@

The implementation of finite sets is presented in
Figure~\ref{fig:typing-finite-set}. It is composed by three
components. First, we define tags as inhabitants of the $\UId$ type. A
tag is solely an informative token, used for display purposes. Finite
sets inhabits the $\EnumU$ type. Unfolding the definition, we get that
a finite set is a list of tags. Finally, elements of a finite set $u$
belong to the corresponding $\EnumT{u}$ type. Intuitively, it
corresponds to an index, a number, pointing to an element of $u$.

@@

In this section, we have developped a type propagation system, based
on bidirectional type-checking. Using bidirectional type-checking as a
boilerplate scrapper is a well-known technique~\cite{}. In our case,
we have shown how to instrument bidirectionality to rationalize the
expressivity of dependent types. We have illustrated our approach with
finite sets. We have successfully abstracted away the low-level
presentation of finite sets, offering a convenient syntax instead.

>>>>

\subsection{Finite sets}
\label{sec:finite-sets}

@@

The specification of finite sets is presented in
Figure~\ref{fig:typing-finite-set}. It is composed by three
components. First, we define tags as inhabitants of the $\UId$ type. A
tag is solely an informative token, used for display purposes. Finite
sets inhabits the $\EnumU$ type. Unfolding the definition, we get that
a finite set is a list of tags. Finally, elements of a finite set $u$
belong to the corresponding $\EnumT{u}$ type. Intuitively, it
corresponds to an index, a number, pointing to an element of $u$.

@@

In this section, we have developped a type propagation system, based
on bidirectional type-checking. Using bidirectional type-checking as a
boilerplate scrapper is a well-known technique~\cite{who?}. In our case,
we have shown how to instrument bidirectionality to rationalize the
expressivity of dependent types. We have illustrated our approach with
finite sets. We have successfully abstracted away the low-level
presentation of finite sets, offering a convenient syntax instead.
